Long term cloud enhancement events of global solar irradiance over Thessaloniki, Greece

### 2024-06-11 article/article.Rmd
Commit 2024-06-11 12:14

header-includes:
  - \usepackage{caption}
  - \usepackage{placeins}
  - \captionsetup{font=small}

@@

An example of CE identification for a selected day is given, in the Appendix
(Figure\nobreakspace{}\ref{fig:example-day}), where the clear sky reference
irradiance and the CE and ECE identification thresholds are shown along with the
actual GHI measurements.  Similar, we provided an example plot of data for one year,
where the relation of the GHI and clear sky reference is shown, along with the OIR
intensity (Appendix Figure\nobreakspace{}\ref{fig:example-year}).

@@

```{r example-year, echo=FALSE, fig.cap="Example scatter plot of the measured GHI and the reference clear sky irradiance for the year 2005. The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black.", fig.pos='H'}
knitr::include_graphics("../images/example-years-13.png")
```

@@

Our dataset, after the data selection processing, consists of
`r ST_total$wattGLB.N` records of GHI measurements, of which
$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ were identified as CE events and
$`r round(100*ST_extreme_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ as ECE events.
The highest recorded GHI due to CE was
$`r round(ST_daily[which.max(wattGLB.max), wattGLB.max],1)`\,\text{W}/\text{m}^2$
on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`, and had
the maximum value of OIR at $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 1)`\,\text{W}/\text{m}^2$.
<!-- The absolute strongest CE event had an OIR of 
<!-- $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 2)`\,\text{W}/\text{m}^2$ on
<!-- `r strftime(ST_daily[which.max(GLB_diff.max), Date], "%d\\ %B %Y")`. -->
The relative stronger CE event was 
$`r round(100*ST_daily[which.max(GLB_ench.max), GLB_ench.max],1)`\,\%$ above the 
clear sky threshold, on 
`r strftime(ST_daily[which.max(GLB_ench.max), Date], "%d\\ %B %Y")`.

## Long term trends

@@

```{r P-energy-mean, echo=FALSE, fig.cap="Trends of the mean OIR per CE."}
knitr::include_graphics("../images/P-energy-3.png")
```

@@

```{r P-energy-N, echo=FALSE, fig.cap="Trend of yearly cloud enhancement occurrences."}
knitr::include_graphics("../images/P-energy-2.png")
```

@@

```{r P-energy-sum, echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"}
knitr::include_graphics("../images/P-energy-1.png")
```

@@

>>>>

header-includes:
  - \usepackage{caption}
  - \usepackage{placeins}
  - \captionsetup{font=small}
  - \usepackage{subcaption}

@@

An example of CE identification for a selected day is given, in the
Figure\nobreakspace{}\ref{fig:example-day}, where the daily course of the clear sky
reference irradiance and the CE and ECE identification thresholds are shown along
with the actual GHI measurements.  In addition, we provide an example scatter plot
between the measured and the modeled clear-sky irradiance for one year, where the CE
and ECE events are clearly grouped above the threshold of irradiance
(Figure\nobreakspace{}\ref{fig:example-year}).

@@

```{r example-year, echo=FALSE, fig.cap="Example scatter plot of the measured GHI and the reference clear sky irradiance for the year 2005. The over-irradiance for CE and ECE events is color coded, while the remaining data points are shown in black.", fig.pos='H'}
knitr::include_graphics("../images/P-example-years-13.png")
```

@@

Following the application of the above discussed methodology to the entire dataset 
(`r round(ST_total$wattGLB.N / 10^6,1)` million one-minute GHI measurements),
$`r round(100*ST_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ were identified as CE events and
$`r round(100*ST_extreme_total$GLB_diff.N_pos/ST_total$wattGLB.N, 3)`\,\%$ as ECE events.
The highest recorded GHI due to CE was
$`r round(ST_daily[which.max(wattGLB.max), wattGLB.max],1)`\,\text{W}/\text{m}^2$
on `r strftime(ST_daily[which.max(wattGLB.max), Date], "%d\\ %B %Y")`, corresponding
to OIR of $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 1)`\,\text{W}/\text{m}^2$.
<!-- The absolute strongest CE event had an OIR of 
<!-- $`r round(ST_daily[which.max(GLB_diff.max), GLB_diff.max], 2)`\,\text{W}/\text{m}^2$ on
<!-- `r strftime(ST_daily[which.max(GLB_diff.max), Date], "%d\\ %B %Y")`. -->
The stronger CE event of
$`r round(100*ST_daily[which.max(GLB_ench.max), GLB_ench.max],1)`\,\%$ above the 
clear sky threshold was observed on 
`r strftime(ST_daily[which.max(GLB_ench.max), Date], "%d\\ %B %Y")`.
In the following sections we are discussing the long-term trends and variability of the CE events as well as of the corresponding OIR and excess irradiation .

## Long-term trends

@@

<!-- ```{r P-energy-mean, echo=FALSE, fig.cap="Trends of the mean OIR per CE."} -->
<!-- knitr::include_graphics("../images/P-energy-3.png") -->
<!-- ``` -->

@@

<!-- ```{r P-energy-N, echo=FALSE, fig.cap="Trend of yearly cloud enhancement occurrences."} -->
<!-- knitr::include_graphics("../images/P-energy-2.png") -->
<!-- ``` -->

@@

<!-- ```{r P-energy-sum, echo=FALSE, fig.cap="Trend of the yearly excess energy due to CE over irradiance"} -->
<!-- knitr::include_graphics("../images/P-energy-1.png") -->
<!-- ``` -->

@@

\begin{figure}[h!]
        {\centering 
            \subfloat[All skies.\label{fig:cusumnotrendmonthly-1}]
                {\includegraphics[width=\linewidth]{../images/P-energy-3} }\\
            \subfloat[Clear skies.\label{fig:cusumnotrendmonthly-2}]
                {\includegraphics[width=\linewidth]{../images/P-energy-2} }\\
            \subfloat[Cloudy skies.\label{fig:cusumnotrendmonthly-3}]
                {\includegraphics[width=\linewidth]{../images/P-energy-1} }
        }
    \caption{Time series for the period 1992 -- 2023 of (a) the yearly CE number of occurrences, (b) the yearly mean OIR and (c) the yearly excess irradiation. The black lines represent the linear trends on the yearly data.}\label{fig:cusumnotrendmonthly}
\end{figure}
